Generalization Errors of Hard Parameter Sharing: High-dimensional Asymptotics and Implications

### 2020-09-24 arxiv/implications.tex
wip
revise+

\section{Implications}\label{sec_special}

@@

It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.We formalize this connection in the above isotropic setting, where we can perform explicit calculations. The prediction loss of MTL has been given in Corollary \ref{cor MTL loss}. We can also calculate the prediction STL easily using Fact \ref{lem_minv} (ii). The proof of the following claim will be given in Section \ref{app_iso_cov}.
\begin{claim}
Under the above isotropic setting for task two, we have that with high probability,
\begin{align*}
	 L(\hat{\beta}_2^{\STL}) = \frac{\sigma^2}{ \rho_2-1}  +\OO(p^{-c}\sigma^2 )
	 \end{align*}
	 for any constant $c\in (0,1/2)$.
\end{claim}

>>>>

\section{Illustrative Examples}\label{sec_special}

@@

It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness. We formalize this connection in the above isotropic setting, where we can perform explicit calculations. The prediction loss of MTL has been given in Corollary \ref{cor MTL loss}. We can also calculate the prediction STL easily using Fact \ref{lem_minv} (ii). The proof of the following claim will be given in Section \ref{app_iso_cov}.
\begin{claim}
Under the above isotropic setting for task two, we have that with high probability,
\begin{align*}
	 L(\hat{\beta}_2^{\STL}) = \frac{\sigma^2}{ \rho_2-1}  +\OO(p^{-c}\sigma^2 )
	 \end{align*}
	 for any constant $c\in (0,1/2)$.
\end{claim}
